Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-06 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
Substantial edits to detector validation, intro, and GD sections

Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of more than 1700 headcam videos collected at home from three children along a span of 6 to 32 months of age—--the SAYCam dataset [@SAYcam]. We thus analyze the video data from this dense, longitudinal dataset as case studies of how the social information in the infant view changes over the course of development. These kinds of longitudinal case studies provide an important counterpoint to cross-sectional investigations for several reasons. By repeatedly recording data from the same child, they allow us to investigate developmental changes within each child and to relate these to developmental milestones (e.g., the onset of walking). Second, they eliminate several nuance sources of variability (e.g., parent/child familiarity with camera, home environment) that may obscure fine-grained developmental patterns.

@@

@@

To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint. 
Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints. 
In prior work examining egocentric videos taken from the infant perspective during in-lab play sessions, OpenPose performed comparably to other modern face detection models [@long2021automated].
However, these at-home, naturalistic videos contain more cluttered visual environments, challenging lighting conditions, and many different novel viewpoints.
This this paper, we first validate the use of OpenPose by comparing face and hand detections to a human-annotated set of 24,000 frames. Overall, we find that OpenPose operates relatively on egocentric scenes including multiple people, even if they are partially-occluded (see Figure 1), nd and discuss the benefits and drawbacks of this automated annotation strategy.

We next capitalize on this computational advance to annotate the entirety of this large, longitudinal video dataset. We use these detections to report how the proportion of faces and hands changes with age and motor development milestones in each of the three children in the dataset. 
Weinvestigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the head cameras as well as a diversity of locations in which videos were recorded.
Finally, making use of automated annotation of pose bounding boxes, we analyze the size, location, and variability of detected faces and poses across development in these three children.

@@

```{r}
# load all detections for gold sample frames
load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData')) 
```

@@

## Detection Validation
```{r}
# Function to evaluate detectors
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

@@

```{r}
# join human and OP detections
gold_sample <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))

 ## output prfs
 face_performance = return_prf_short(gold_sample$face_eval_ketan)
 hand_performance = return_prf_short(gold_sample$hand_eval_ketan)
```

@@

@@

To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A).  Frames were jointly annotated for the presence of faces and hands by one author. A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was >95%. Upon manually inspecting these 24K frames, we noticed that `r  num_frames_excluded` were sampled from videos taken from the allocentric perspective (i.e., not from the infant viewpoint); these frames and videos containing these frames were subsequently excluded from all other analyses.

@@

To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / (hits + false alarms)), recall (hits / (hits + misses)), and F-score (the harmonic mean of precision and recall).  In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`. For hands, the F-score was `r round(hand_performance[3],2)`, with a precision of `r round(hand_performance[1],2)` and recall of `r round(hand_performance[2],2)`. While face and hand detections showed moderately good precision, face detections were overall slightly more accurate than hand detections. In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.

We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose -- a notoriously challenging detection problem [@bambach2015lending]. To assess this possibility, we obtained additional human annotations for the subsample of 9051 frames in the gold set frames where a hand was present; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands. Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands. When frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`. We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Appendix Figure \ref{fig:handLocation}.

Next, we examined the degree to which the detector confidence changed model performance. We found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`. Overall, our analyses suggested that including all detections was the most beneficial for optimizing precision; see Appendix for a full ROC curve detailing all detector confidence confidence thresholds.

Finally, we examined whether model accuracy for hands and faces varied across age or between child and location  (see plots for age/child in Appendix, Figure \ref{fig:det_perf_by_age}, and location in Figure \ref{fig:det_perf_by_locations}). Some of the videos at taken at older ages for child A did seem to show lower hand detection accuracy, perhaps due the presence of child's hands; however, there were also fewer videos at these time points.  In general, however, we found evidence for considerable variation in model accuracy across different videos, suggesting that particular recording contexts, activities, or lighting could cause conditions that would impair detector performance.

In a qualitative analysis, we also inspected frames where OpenPose failed to detect faces/hands or erroneously detected them to gain insight into the factors driving performance. Figure \ref{fig:error_examples} shows examples of both missed detections and false alarms for both faces and hands and highlights the challenging detection conditions presented by these at-home, naturalistic videos. Many missed faces included very far away or very close up views of faces at odd angles, as well as faces that were partially occluded by odd lighting conditions. False alarms for faces included animal faces depicted in picture books and poses where the person was not facing a camera. Hands were often missed when they were seen only from the side and unconnected to a pose, whereas hands were sometimes erroneously detected when a pose was present but the hands were out of view. Thus, while OpenPose was trained on photographs from the adult perspective, this model still performed relatively well on these challenging the egocentric infant viewpoint with no fine-tuning or post-processing of the detections, especially given these challenging and varied videos.

@@

Finally, we analyzed how these two sources of social information co-occurred.
To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range. Faces and hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}C). As shown in Figure \ref{fig:faceHandContingency}, all three infants were more likely to see hands independently -- without the presence of a face -- than they were likely to see faces independently. That is, generally speaking when a face was present, a hand also tended to be present.

@@

## Variability with motor development milestones
How does the social information in view change as a function of motor development? One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2016infant] relative to infants who are still sitting and crawling.  Indeed, in in-lab studies, research has found that children's in-the-moment posture -- and that of their caregiver -- is a strong predictor of the visual social information in view [@franchak2017see; @long2021automated].

We thus next analyzed how the social information in view changed as a function of each child reaching particular developmental motor milestones. Each parent completed the Ages and Stages Questionnaire (ASQ) [@bricker1999ages], which includes questions about their child's motor abilities, and we used the responses from this questionnaire to code the age (in months) at which each child became able to sit, cruise, and walk on their own (questions about crawling were not included in the questionnaire)..  We found considerable variability in the age at which each child achieved these three milestones. Participants S and A were already able to sit at 6 months of age, while Y began achieving this milestone at 8 months. A was able to cruise at 9 months of age, while S reached that milestone at 10 months, with Y just behind. Learning to walk showed the most variation, with S walking after 10 months, A after 13 months, and Y after 16 months of age.

We then used a discontinuity analysis to estimate whether the onset of each of these three motor milestones changed the proportion of faces/hands in each chid's view. Specifically, we used mixed-effects regressions with per-child random intercepts to estimate whether children's age (in months), each motor milestone, and their interaction significantly influenced the proportion of hands or faces that each child saw; see Appendix for tables with full model specifications and tables with all coefficients. Overall, we found that the age at which these children began sitting did not significantly predict changes in either the amount of faces or hands that they saw. However, as children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$), suggesting that the ability to be upright and locomote even somewhat independently was sufficient to significantly change children's visual social environment. For faces, however, there was also a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$). However, we did not find major differences with the onset of walking; as these children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$). Thus, these analyses confirm and extend cross-sectional finding, leveraging dense, within-child data to help elucidate the complex relationship between motor development and the social information in view.

@@

How does the child's context influence the social information in view? 
@bruner1985role discussed the role of children's activities in shaping the information present for learning. Following this idea, we investigated whether there were differences in access to faces and hands by the activity that the child was engaged in. This hypothesis seems intuitively appealing. Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime). 
We did not have access to annotations of activity. 
Thus, following @roy2015predicting, we used spatial location as a proxy for activity context, taking advantage of the presence of these annotations for a subset of the SAYCam videos. 
Of the `r num_videos` videos in the dataset, `r num_videos_annotated` were annotated for the location or locations they were filmed in. 
These location annotations were only available for two children, S and A.
Annotated locations mostly consisted of rooms of the house (e.g., "living room") but also included some other locations (e.g., "car," "outside").
Of this set, `r videos_included` videos were filmed in only a single location (e.g., the location label did not change within the video), representing 17 percent of the dataset and over 5 million frames. 
In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room. However, every location was of course associated with multiple activities; see Appendix Figure \ref{fig:activities_by_loc} for a heatmap relating individual activities to locations in the dataset.

@@

cowplot::plot_grid(eye_dist_plot, CV_faces_plot, rel_widths=c(1,2))
```
In a third set of analyses, we explored fine-grained changes in the SAYCam infants' access to social information across development.
In these analyses, we capitalize on the fact that OpenPose provides not only face and hand detections but also positional keypoints. 
In particular, we explored this keypoint dataset with the idea that greater mobility allows older children to be further from their caregivers on average. 
Thus, younger, less mobile children may tend to see larger faces towards the center of their visual field while older, more mobile children may experience more smaller, more variable views of faces.
The same dynamic would be predicted hold for hands as well, as it would be driven by overall differences in distance.

@@

# General Discussion
Here, we first validated the use of an automated pose detection model to detect the faces and hands in view in a longitudinal dataset of egocentric, everyday visual experience. We then used these detections to analyze the social information seen from each of three children's egocentric perspective from 6 to 32 months of age.

@@

Second, we also found an unexpectedly high proportion of hands in infants' view, even when restricting the analysis to detections in the center field-of-view to make the viewpoints comparable to those of headcams used in prior work and to exclude the portion of the frame most likely to contain children's own hands.
Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. 
During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). 
Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. 
Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

@@

Nonetheless, we believe that these advances in datasets and methodologies represent a step in the right direction. 
The present paper demonstrates the feasibility of using a modern computer vision model to annotate the entirety of a very large dataset (here, >42M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to human annotations in prior work. 
While OpenPose did not provide annotations that were as accurate as those provided by human annotators, we found relatively consistent results with prior literature, suggesting that the sheer scale and density of the annotations provided by this method may overcome some of its limitations.

Importantly, however, these automated detections do not entirely obviate the need for careful inspection and manual annotation of dense video data. While the present results suggest that OpenPose achieves moderate performance at detecting faces and hands in egocentric videos -- as does @Long2021automated -- these results do not guarantee that OpenPose will generalize with similar accuracy to other video datasets. By using manual annotations to estimate the accuracy of these automated techniques for their video datasets, researchers can weigh the pros and cons of automated detections for answering their particular research questions. While OpenPose does provide a considerable amount of about all of the people in a given image -- estimating the entire poses for every individual -- it may not always perform similarly in challenging viewpoints.

So, how might OpenPose -- or other pose detection algorithms -- be improved upon and used in future work? One promising direction may be to use detailed pose annotations of the people in the infant view to fine-tune later layers of pose detection networks. This has the potential to improve upon the overall accuracy of the network to detect the social information in infant egocentric videos. Standard computer vision models are rarely trained on the egocentric viewpoint, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors. A second potential area for innovation lies in leveraging the dense nature of these large-scale annotations to improve model accuracy: By pooling detections from surrounding frames, we may be able to build classifiers that perform more accurately on a single challenging viewpoint. Finally, a third area for improvement consists of building classifiers that can accurately distinguish between children's hands (as seen from the egocentric point of view) versus adults' hands--a notoriously challenging problem in computer vision [@bambach2017lending]. We expect that these goals may become more and more feasible as we simultaneously improve the head-mounted cameras that are used in both at-home and in-lab studies; increasing the resolution and quality of the images we record will no doubt improve the ability of computer vision algorithms to extract detailed information from them.

>>>>

Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of more than 1700 headcam videos collected at home from three children along a span of 6 to 32 months of age—--the SAYCam dataset [@SAYcam]. We analyze the video data from this dense, longitudinal dataset as case studies of how the social information in the infant view changes over the course of development in individual children. These kinds of longitudinal case studies provide an important counterpoint to cross-sectional investigations for several reasons. By repeatedly recording data from the same child, they allow us to investigate developmental changes within each child and to relate these to developmental milestones (e.g., the onset of walking). Second, they eliminate several nuance sources of variability (e.g., parent/child familiarity with camera, home environment) that may obscure fine-grained developmental patterns.

@@

However, it is important to note that these data -- albeit naturalistic and densely sampled within individuals -- come from only a few children in western contexts [@@henrich2010most], and as such cannot on their own yield generalizable conclusions about developmental changes in the infant view. Instead, they serve as a testbed for validating prior developmental findings within the daily lives of individual children -- and for generating novel hypotheses that can be tested in cross-sectional datasets or targeted in-lab experiments.

@@

To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint. 
Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints. 
In prior work examining egocentric videos taken from the infant perspective during in-lab play sessions, OpenPose performed comparably to other modern face detection models [@long2021automated].
However, these at-home, naturalistic videos contain more cluttered visual environments, challenging lighting conditions, and many different novel viewpoints.
In this paper, we first validate the use of OpenPose by comparing face and hand detections to a human-annotated set of 24,000 frames. Though OpenPose does not detect faces and hands with perfect accuracy, we find that this model still operates relatively well on these challenging egocentric scenes including multiple people, even if they are partially-occluded (see Figure 1 for example detections and Appendix Figure \ref{fig:error_examples} for examples of missed detections and false alarms).

We thus capitalize on this computational advance to annotate the entirety of this large, longitudinal video dataset. 
We use these detections to first report how the proportion of faces and hands changes with age and motor development milestones in each of the three children in the dataset. 
We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the head cameras as well as a diversity of locations in which videos were recorded.
Finally, making use of automated annotation of pose bounding boxes, we analyze the size, location, and variability of detected faces and poses across development in these three children.
Overall, these findings largely validate prior cross-sectional findings, and further suggest that automated annotated can be used to analyze naturalistic video datasets to build towards generalizable conclusions about the statistics of the social information in the infant view across a wide variety of populations.

@@

```{r}
# load all detections for gold sample frames
load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_with_centerall_detections.RData')) 
```

@@

## Detector Validation
```{r}
# Function to evaluate detectors
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

@@

```{r}
# join human and OP detections
gold_sample <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
   mutate(face_eval_ketan_center = evaluate_detector(face_present_ketan, face_detected_center), hand_eval_ketan_center = evaluate_detector(hand_present_ketan, hand_detected_center))

 ## output prfs
 face_performance = return_prf_short(gold_sample$face_eval_ketan)
 hand_performance = return_prf_short(gold_sample$hand_eval_ketan)

 face_performance_center = return_prf_short(gold_sample$face_eval_ketan_center)
 hand_performance_center = return_prf_short(gold_sample$hand_eval_ketan_center)
```

@@

gold_sample_child_hands <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  filter(child_hand_seg==TRUE)

@@

@@

### Detector vs. human annotations of faces/hands
To test the validity of OpenPose's hand and face detections, we compared the accuracy detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); this sample was conducted before child Y was added to the dataset.  Frames were jointly annotated for the presence of faces and hands by one author. A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was >95%. Upon manually inspecting these 24K frames, we noticed that `r  num_frames_excluded` were sampled from videos taken from the allocentric perspective (i.e., not from the infant viewpoint); these frames and videos containing these frames were subsequently excluded from all other analyses.

To evaluate OpenPose's performance, we compared its detections to the manually-annotated "gold set" of frames, calculating precision (hits / (hits + false alarms)), recall (hits / (hits + misses)), and F-score (the harmonic mean of precision and recall).  In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`. For hands, the F-score was `r round(hand_performance[3],2)`, with a precision of `r round(hand_performance[1],2)` and recall of `r round(hand_performance[2],2)`. While face and hand detections showed moderately good precision, face detections were overall slightly more accurate than hand detections. In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.

We next inspected frames where OpenPose failed to detect faces/hands or erroneously detected them to gain insight into the factors driving performance. Appendix Figure \ref{fig:error_examples} shows randomly sampled examples of both missed detections and false alarms for both faces and hands and highlights the challenging detection conditions presented by these at-home, naturalistic videos. Many missed faces included very far away or very close up views of faces at odd angles, as well as faces that were partially occluded by odd lighting conditions. False alarms for faces included animal faces depicted in picture books and poses where the person was not facing a camera. Hands were sometimes erroneously detected when a pose was present but the hands were out of view, and hands were often missed when they were seen only from the side and unconnected to a pose or belonged to the child.

### Detecting children's own hands 
We thus suspected that OpenPose's low recall for hands in this dataset was because children’s own hands were often in view of the camera and unconnected to a pose -- a notoriously challenging detection problem [@bambach2015lending]. To assess this possibility, we obtained additional human annotations for the subsample of 9051 frames in the gold set frames where a hand was present; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands. Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands; OpenPose was only able to detect children's hands when there were in view `r round(mean(gold_sample_child_hands$hand_detected),2)*100`% of the time. Accordingly, when frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`. We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Appendix Figure \ref{fig:handLocation}.

### Restricting detections to the center field-of-view
Given that the fish-eye lens may have distorted the edges of the visual field in the videos, we also examined whether we would see improved precision by restricting the included detections to the center field-of-view, and excluding detections that occured in the outer 20\% of each frame. This restricted field-of-view is also more comparable to video data from other head-mounted cameras. However, we found that excluding these detections did not improve the model's precision for either faces or hands; rather, it only decreased recall. Excluding peripehral detections led to an overall f-score of `r round(face_performance_center[3],2)`, for faces with a precision of `r round(face_performance_center[1],2)` and recall of `r round(face_performance_center[2],2)`. For hands, the F-score for center detections was `r round(hand_performance)center[3],2)`, with a precision of `r round((hand_performance)[1],2)` and recall of `r round((hand_performance)[2],2)`. Thus, detections that were made in the periphery of these videos were not more likely to be false alarms for either faces or hands. Appendix Figure \ref{fig: density-op-fps} illustrates this finding, showing the density of false positives for both faces and hands that are concentrated in the center of the fied of view.

### Detector confidence
We next examined the degree to which including detections that the model was more or less confident in changed overall model performance for face/hand detection. When we restricted detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`. Further analyses sweeping across the entire range of possible confidence detection thresholds revealed that including all detections was the most beneficial for optimizing the rate of true positives (see Appendix Figure \ref{fig:roc_curves} for full ROC curves for both face and hand detections).

### Accuracy across child, location, and age
Finally, we examined whether model accuracy for hands and faces varied across age or between child and the location in which the videos were filmed (e.g., kitchen vs. living room). Some of the videos at taken at older ages for child A did seem to show lower hand detection accuracy, perhaps due the presence of child's hands; however, there were also fewer videos at these time points (see plots for age/child in Appendix, Figure \ref{fig:det_perf_by_age}). We did not find any discernible trends in face/hand detection accuracy across different filming locations (see Figure \ref{fig:det_perf_by_locations}). However, we did still see considerable variation in model accuracy across different videos, suggesting that particular recording activities, lighting conditions, or situations could cause conditions that would impair detector performance.

Thus, while OpenPose was trained on photographs from the adult perspective, this model still performed relatively well on these challenging the egocentric infant viewpoint with no fine-tuning or post-processing of the detections, especially given these challenging and varied videos. Including all detections made by OpenPose in all locations led to the most accurate model performance. We next use this detection method to analyze the rest of the large dataset, with the caveat that we are likely underestimating the proportion of hands in the infant view.

@@

Finally, we analyzed how these two sources of social information co-occurred.
To do so, wecalculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range. Faces and hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}C). As shown in Figure \ref{fig:faceHandContingency}, all three infants were more likely to see hands independently -- without the presence of a face -- than they were likely to see faces independently. That is, generally speaking when a face was present, a hand also tended to be present.

@@

## Variability with motor development milestones
How does the social information in view change as a function of motor development? One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2016infant] relative to infants who are still sitting and crawling.  Indeed, in in-lab studies, children's in-the-moment posture -- and that of their caregiver -- is a strong predictor of the visual social information that children see [@franchak2017see; @long2021automated].

We thus next analyzed how the social information in view changed as a function of each child reaching particular developmental motor milestones. Each parent in the SAYCam dataset completed the Ages and Stages Questionnaire (ASQ) [@bricker1999ages], which includes questions about their child's motor abilities, and we used the responses from this questionnaire to code the age (in months) at which each child became able to sit, cruise, and walk on their own (questions about crawling were not included in the questionnaire). We found considerable variability in the age at which each child achieved these three milestones. Participants S and A were already able to sit at 6 months of age, while Y began achieving this milestone at 8 months. A was able to cruise at 9 months of age, while S reached that milestone at 10 months, with Y just behind. Learning to walk showed the most variation, with S walking after 10 months, A after 13 months, and Y after 16 months of age.

We then used a discontinuity analysis to estimate whether the onset of each of these three motor milestones changed the proportion of faces/hands in each chid's view. Specifically, we used mixed-effects regressions with per-child random intercepts to estimate whether children's age (in months), each motor milestone, and their interaction significantly influenced the proportion of hands or faces that each child saw; see Appendix for tables with full model specifications and tables with all coefficients. Overall, we found that the age at which these children began sitting did not significantly predict changes in either the amount of faces or hands that they saw. However, as children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$), suggesting that the ability to be upright and locomote even somewhat independently was sufficient to significantly change children's visual social environment. For faces, however, there was also a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$). However, we did not find major differences with the onset of walking; as these children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$). Thus, these analyses confirm and extend cross-sectional findings, leveraging dense, within-child data to help elucidate the complex relationship between motor development and the social information in view.

@@

How does the child's context influence the social information in view? 
@bruner1985role discussed the role of children's activities in shaping the information present for learning. Following this idea, we investigated whether there were differences in access to faces and hands by the activity that the child was engaged in. This hypothesis seems intuitively appealing. Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime). 
We did not have access to detailed annotations of activity; each video was associated with several different activities. 
Thus, following @roy2015predicting, we used spatial location as a proxy for activity context, taking advantage of the presence of these annotations for a subset of the SAYCam videos. 
In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room. However, every location was associated with multiple activities; see Appendix Figure \ref{fig:activities_by_loc} for a heatmap relating individual activities to locations in the dataset.
Of the `r num_videos` videos in the dataset, `r num_videos_annotated` were annotated for the location or locations they were filmed in. 
These location annotations were only available for two children, S and A.
Annotated locations mostly consisted of rooms of the house (e.g., "living room") but also included some other locations (e.g., "car," "outside").
Of this set, `r videos_included` videos were filmed in only a single location (e.g., the location label did not change within the video), representing 17 percent of the dataset and over 5 million frames.

@@

cowplot::plot_grid(eye_dist_plot, CV_faces_plot, rel_widths=c(1,2))
```
In a final set of analyses, we explored fine-grained changes in the SAYCam infants' access to social information across development.
In these analyses, we capitalize on the fact that OpenPose provides not only face and hand detections but also positional keypoints. 
In particular, we explored this keypoint dataset with the idea that greater mobility allows older children to be further from their caregivers on average. 
Thus, younger, less mobile children may tend to see larger faces towards the center of their visual field while older, more mobile children may experience more smaller, more variable views of faces.
The same dynamic would be predicted hold for hands as well, as it would be driven by overall differences in distance.

@@

# General Discussion
Here, we validated the use of an automated pose detection model to detect the faces and hands in view in a longitudinal dataset of egocentric, everyday visual experience. We then used these detections to analyze the social information seen from each of three children's egocentric perspective from 6 to 32 months of age.

@@

Second, we also found an unexpectedly high proportion of hands in the egocentric experience of these three infants. We found this to be true even when restricting the analysis to detections in the center field-of-view to make the viewpoints comparable to those of headcams used in prior work and to exclude the portion of the frame most likely to contain children's own hands.
Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. 
During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). 
Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. 
Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

@@

Nonetheless, we believe that these advances in datasets and methodologies represent a step in the right direction. 
The present paper demonstrates the feasibility of using a modern computer vision model to annotate the entirety of a very large dataset (here, >42M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to human annotations in prior work. 
While OpenPose did not provide annotations that were as accurate as those provided by human annotators, we found relatively consistent results with prior literature, suggesting that the sheer scale and density of the annotations provided by this method may overcome some of its limitations. 
Thus, OpenPose may alleviate the burden of manually annotating large egocentric video datasets for the social information in view, helping the field build more generalizable conclusions about how infants experience their early visual social environment.

Of course, these automated detections do not entirely obviate the need for careful inspection and manual annotation of dense video data. While the present results suggest that OpenPose achieves moderate performance at detecting faces and hands in infant egocentric videos -- as in @Long2021automated -- these results do not guarantee that OpenPose will generalize with similar accuracy to other video datasets.   While OpenPose does provide a considerable amount of about all of the people in a given image -- estimating the entire poses for every individual -- it may not perform accurately enough to answer certain fine-grained research questions. Going forward, we suggest that researchers continue to compare a small set of manual annotations relevant to their research questions of interest to OpenPose's performance.

How might pose detection algorithms be improved upon such that they can achieve greater accuracy in analyzing infant egocentric videos?  This question is ripe for collaboration between computer vision experts and devleopmental psychologists. One promising direction may be to use detailed pose annotations of the people in the infant view to fine-tune later layers of pose detection networks. This has the potential to improve upon the overall accuracy of the network to detect the social information in infant egocentric videos. Standard computer vision models are rarely trained on the egocentric viewpoint, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors. A second potential area for innovation lies in leveraging the dense nature of these large-scale annotations to improve model accuracy: By pooling detections from surrounding frames, we may be able to build classifiers that perform more accurately on a single challenging viewpoint. Finally, a third area for improvement consists of building classifiers that can accurately distinguish between children's hands (as seen from the egocentric point of view) versus adults' hands--a notoriously challenging problem in computer vision [@bambach2015lending]. We expect that these goals may become more and more feasible as we also improve the head-mounted cameras that are used in both at-home and in-lab studies; increasing the resolution and quality of the images we record will no doubt improve the ability of computer vision algorithms to extract detailed information.
